### 2025-01-18 paper/icml25/first/sects/ablation.tex
added discovery-ablation figures, added hyperparameter tables & script
figures are now generated in a grid

\begin{figure*}[!t]
    \centering
    \begin{subfigure}[b]{0.32\textwidth}
        \includegraphics[width=\textwidth]{figs/dispersion-ablation-1-mlp.pdf}
        \caption{Dispersion, MLP, 1 agent}
        \label{fig:dispersion-ablation-mlp-1}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \includegraphics[width=\textwidth]{figs/dispersion-ablation-3-transformer.pdf}
        \caption{Dispersion, Transformer, 3 agents}
        \label{fig:dispersion-ablation-transformer-3}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \includegraphics[width=\textwidth]{figs/dispersion-ablation-5-transformer.pdf}
        \caption{Dispersion, Transformer, 5 agents}
        \label{fig:dispersion-ablation-transformer-5}
    \end{subfigure}

    \begin{subfigure}[b]{0.32\textwidth}
        \includegraphics[width=\textwidth]{figs/transport-ablation-1-mlp.pdf}
        \caption{Transport, MLP, 1 agent}
        \label{fig:transport-ablation-mlp-1}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \includegraphics[width=\textwidth]{figs/transport-ablation-3-transformer.pdf}
        \caption{Transport, Transformer, 3 agents}
        \label{fig:transport-ablation-transformer-3}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \includegraphics[width=\textwidth]{figs/transport-ablation-5-transformer.pdf}
        \caption{Transport, Transformer, 5 agents}
        \label{fig:transport-ablation-transformer-5}
    \end{subfigure}

>>>>

\begin{figure*}[!t]
    \centering
    \begin{subfigure}[b]{0.30\textwidth}
        \includegraphics[width=\textwidth]{figs/dispersion-ablation-1-mlp.pdf}
        \caption{Dispersion, MLP, 1 agent}
        \label{fig:dispersion-ablation-mlp-1}
    \end{subfigure}
    \begin{subfigure}[b]{0.30\textwidth}
        \includegraphics[width=\textwidth]{figs/dispersion-ablation-3-transformer.pdf}
        \caption{Dispersion, Transformer, 3 agents}
        \label{fig:dispersion-ablation-transformer-3}
    \end{subfigure}
    \begin{subfigure}[b]{0.30\textwidth}
        \includegraphics[width=\textwidth]{figs/dispersion-ablation-5-transformer.pdf}
        \caption{Dispersion, Transformer, 5 agents}
        \label{fig:dispersion-ablation-transformer-5}
    \end{subfigure}

    \begin{subfigure}[b]{0.30\textwidth}
        \includegraphics[width=\textwidth]{figs/transport-ablation-1-mlp.pdf}
        \caption{Transport, MLP, 1 agent}
        \label{fig:transport-ablation-mlp-1}
    \end{subfigure}
    \begin{subfigure}[b]{0.30\textwidth}
        \includegraphics[width=\textwidth]{figs/transport-ablation-3-transformer.pdf}
        \caption{Transport, Transformer, 3 agents}
        \label{fig:transport-ablation-transformer-3}
    \end{subfigure}
    \begin{subfigure}[b]{0.30\textwidth}
        \includegraphics[width=\textwidth]{figs/transport-ablation-5-transformer.pdf}
        \caption{Transport, Transformer, 5 agents}
        \label{fig:transport-ablation-transformer-5}
    \end{subfigure}

    \begin{subfigure}[b]{0.30\textwidth}
        \includegraphics[width=\textwidth]{figs/discovery-ablation-1-mlp.pdf}
        \caption{Discovery, MLP, 1 agent}
        \label{fig:discovery-ablation-mlp-1}
    \end{subfigure}
    \begin{subfigure}[b]{0.30\textwidth}
        \includegraphics[width=\textwidth]{figs/discovery-ablation-3-transformer.pdf}
        \caption{Discovery, Transformer, 3 agents}
        \label{fig:discovery-ablation-transformer-3}
    \end{subfigure}
    \begin{subfigure}[b]{0.30\textwidth}
        \includegraphics[width=\textwidth]{figs/discovery-ablation-5-transformer.pdf}
        \caption{Discovery, Transformer, 5 agents}
        \label{fig:discovery-ablation-transformer-5}
    \end{subfigure}

    \begin{subfigure}[b]{0.30\textwidth}
        \includegraphics[width=\textwidth]{figs/sampling-ablation-1-mlp.pdf}
        \caption{Discovery, MLP, 1 agent}
        \label{fig:sampling-ablation-mlp-1}
    \end{subfigure}
    \begin{subfigure}[b]{0.30\textwidth}
        \includegraphics[width=\textwidth]{figs/sampling-ablation-3-transformer.pdf}
        \caption{Discovery, Transformer, 3 agents}
        \label{fig:sampling-ablation-transformer-3}
    \end{subfigure}
    \begin{subfigure}[b]{0.30\textwidth}
        \includegraphics[width=\textwidth]{figs/sampling-ablation-5-transformer.pdf}
        \caption{Discovery, Transformer, 5 agents}
        \label{fig:sampling-ablation-transformer-5}
    \end{subfigure}

### 2025-01-18 paper/icml25/first/sects/experiments.tex
figures are now generated in a grid

\begin{figure*}[!t]
    \centering
    \begin{subfigure}[b]{0.32\textwidth}
        \includegraphics[width=\textwidth]{figs/dispersion-1-mlp.pdf}
        \caption{Dispersion, MLP, 1 agent}
        \label{fig:dispersion-mlp-1}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \includegraphics[width=\textwidth]{figs/dispersion-3-transformer.pdf}
        \caption{Dispersion, Transformer, 3 agents}
        \label{fig:dispersion-transformer-3}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \includegraphics[width=\textwidth]{figs/dispersion-5-transformer.pdf}
        \caption{Dispersion, Transformer, 5 agents}
        \label{fig:dispersion-transformer-5}
    \end{subfigure}

    \begin{subfigure}[b]{0.32\textwidth}
        \includegraphics[width=\textwidth]{figs/transport-1-mlp.pdf}
        \caption{Transport, MLP, 1 agent}
        \label{fig:transport-mlp-1}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \includegraphics[width=\textwidth]{figs/transport-3-transformer.pdf}
        \caption{Transport, Transformer, 3 agents}
        \label{fig:transport-transformer-3}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \includegraphics[width=\textwidth]{figs/transport-5-transformer.pdf}
        \caption{Transport, Transformer, 5 agents}
        \label{fig:transport-transformer-5}
    \end{subfigure}

    \begin{subfigure}[b]{0.32\textwidth}
        \includegraphics[width=\textwidth]{figs/discovery-1-mlp.pdf}
        \caption{Discovery, MLP, 1 agent}
        \label{fig:discovery-mlp-1}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \includegraphics[width=\textwidth]{figs/discovery-3-transformer.pdf}
        \caption{Discovery, Transformer, 3 agents}
        \label{fig:discovery-transformer-3}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \includegraphics[width=\textwidth]{figs/discovery-5-transformer.pdf}
        \caption{Discovery, Transformer, 5 agents}
        \label{fig:discovery-transformer-5}
    \end{subfigure}

@@

Overall, considering different training algorithms, architectures, scenarios, hyperparameters, we completed a total of $216$ runs lasting between $1$ to $8$ hours each.

>>>>

\begin{figure*}[!t]
    \centering
    \begin{subfigure}[b]{0.30\textwidth}
        \includegraphics[width=\textwidth]{figs/dispersion-1-mlp.pdf}
        \caption{Dispersion, MLP, 1 agent}
        \label{fig:dispersion-mlp-1}
    \end{subfigure}
    \begin{subfigure}[b]{0.30\textwidth}
        \includegraphics[width=\textwidth]{figs/dispersion-3-transformer.pdf}
        \caption{Dispersion, Transformer, 3 agents}
        \label{fig:dispersion-transformer-3}
    \end{subfigure}
    \begin{subfigure}[b]{0.30\textwidth}
        \includegraphics[width=\textwidth]{figs/dispersion-5-transformer.pdf}
        \caption{Dispersion, Transformer, 5 agents}
        \label{fig:dispersion-transformer-5}
    \end{subfigure}

    \begin{subfigure}[b]{0.30\textwidth}
        \includegraphics[width=\textwidth]{figs/transport-1-mlp.pdf}
        \caption{Transport, MLP, 1 agent}
        \label{fig:transport-mlp-1}
    \end{subfigure}
    \begin{subfigure}[b]{0.30\textwidth}
        \includegraphics[width=\textwidth]{figs/transport-3-transformer.pdf}
        \caption{Transport, Transformer, 3 agents}
        \label{fig:transport-transformer-3}
    \end{subfigure}
    \begin{subfigure}[b]{0.30\textwidth}
        \includegraphics[width=\textwidth]{figs/transport-5-transformer.pdf}
        \caption{Transport, Transformer, 5 agents}
        \label{fig:transport-transformer-5}
    \end{subfigure}

    \begin{subfigure}[b]{0.30\textwidth}
        \includegraphics[width=\textwidth]{figs/discovery-1-mlp.pdf}
        \caption{Discovery, MLP, 1 agent}
        \label{fig:discovery-mlp-1}
    \end{subfigure}
    \begin{subfigure}[b]{0.30\textwidth}
        \includegraphics[width=\textwidth]{figs/discovery-3-transformer.pdf}
        \caption{Discovery, Transformer, 3 agents}
        \label{fig:discovery-transformer-3}
    \end{subfigure}
    \begin{subfigure}[b]{0.30\textwidth}
        \includegraphics[width=\textwidth]{figs/discovery-5-transformer.pdf}
        \caption{Discovery, Transformer, 5 agents}
        \label{fig:discovery-transformer-5}
    \end{subfigure}

    \begin{subfigure}[b]{0.30\textwidth}
        \includegraphics[width=\textwidth]{figs/sampling-1-mlp.pdf}
        \caption{Discovery, MLP, 1 agent}
        \label{fig:sampling-mlp-1}
    \end{subfigure}
    \begin{subfigure}[b]{0.30\textwidth}
        \includegraphics[width=\textwidth]{figs/sampling-3-transformer.pdf}
        \caption{Discovery, Transformer, 3 agents}
        \label{fig:sampling-transformer-3}
    \end{subfigure}
    \begin{subfigure}[b]{0.30\textwidth}
        \includegraphics[width=\textwidth]{figs/sampling-5-transformer.pdf}
        \caption{Discovery, Transformer, 5 agents}
        \label{fig:sampling-transformer-5}
    \end{subfigure}

@@

Overall, considering different training algorithms, architectures, scenarios, hyperparameters, we completed a total of $254$ runs lasting between $1$ to $8$ hours each.
